### 2016-11-22 conclusion.tex
Added James' comments

In this thesis, we have explored how supernovae, when modeled with a robust,
physically-motivated method, can impact the growth and evolution of galaxies.
We introduced a novel model for SN feedback that takes into account the
important effects of previously ignored physics: the evaporation of cold gas
driven by thermal conduction.  This model allowed us to see how SN can (and
cannot!) regulate the flow of gas into and out of galaxies, where it ultimately
forms stars.  We have also shown that the current $\Lambda CDM$ cosmological
model is consistent with recent observations of galaxy kinematics.

In Chapter 2, we presented a detailed description of the new superbubble model,
and implemented it in the SPH code {\sc Gasoline2}.  We rely on the strongly
self-limiting process of thermal evaporation \citep{Cowie1977}, where cold mass
is evaporated into a hot bubble with a mass flux given by $ \frac{{\rm d
}M_b}{{\rm d}t} = \frac{4\,\pi\mu}{25k_B}\kappa_0\,\frac{\Delta T^{5/2}}{\Delta
x}\ A$. This allows us to develop a new model for SN feedback, that gives
realistic estimates for cooling in unresolved hot bubbles, and accurately
calculates the mass loading of SN energy.  We demonstrated that this model is
insensitive to resolution, unresolved ISM structure, and uncertain (turbulent)
magnetic fields.  Finally, after investigating the behaviour of individual
bubbles, we showed that superbubble feedback was more effective at both
regulating star formation and at driving galactic winds.

Chapter 3 then applied this new model to the cosmological simulation of a Milky
Way like galaxy.  We compared the same galaxy, simulated four times with
different feedback models (no feedback, the older \citet{Stinson2006} blastwave model,
and superbubble feedback with $10^{51}\;\rm{erg}/SN$ and
$2\times10^{51}\;\rm{erg}/SN$).  The results of this comparison found that even
though the galaxy massively overproduced stars (a result previously seen in
\citealt{Stinson2010}) when simulated with blastwave feedback (or no feedback),
the same SN energy, when simulated using our new superbubble model, was able to
produce a realistic stellar mass fraction for the galaxy's entire history.  Not
only did the galaxy simulated with superbubble feedback have the correct
stellar mass, we showed that it also was effectively bulgeless, with a
completely flat rotation curve.  These two results were ultimately caused by the
same process.  At high redshift, superbubble feedback efficiently drives highly
mass loaded winds, expelling gas from the ISM of the galaxy.  As the gas that
forms a stellar bulge was primarily accreted at high redshift, this meant that
these winds preferentially removed low angular momentum material, while
preserving the gas with high angular momentum.  Thus, superbubble
feedback was able to naturally prevent both runaway star formation and the
formation of a bulge through these winds.

Chapter 4 took these results to the limit to examine whether SN alone are able
to regulate the formation of stars in galaxies both heavier and lighter than the
Milky Way.  By creating a new sample of 18 simulated galaxies (the
McMaster Unbiased Galaxy Simulations 2), we were able to demonstrate a critical
mass at which SN feedback breaks down as a regulator of gas accretion and star
formation.  Galaxies that exceed this mass, $(\sim 10^{12}\;\Msun)$, will produce
more stars than real galaxies, and produce much of these stars in a dense
stellar bulge.  All of this arises due to a fundamental relation between the
mass loading of superbubble driven winds and the mass of the galaxy (either its
halo or its disc).  When the escape velocity of the disc exceeds the sound speed
of superbubble-heated gas (which has a typical mass loading of $\eta=10$), only
outflows which have entrained less material are able to escape the galaxy,
leading to decreasing efficiency in ejecting material, and a shutdown of
SN regulation.  The fact that this shutdown occurs exactly where powerful AGN
are observed, and that it results in a vigorous transport of gas to the nucleus
of the galaxy make this result strong evidence that this shutdown acts as a kind
of ``hand-off'' between SN and AGN feedback.

Chapter 5 applied the MUGS2 sample of galaxies we produced in
\citet{Keller2016a} and used them to examine the radial acceleration relation
(RAR) that was derived by \citet{McGaugh2016} from observations of the SPARC
\citep{Lelli2016} catalog.  Contrary to the assertions of some
\citep{Milgrom2016}, the tight relation seen in the SPARC data does not require
new fundamental physics (such as self-interacting dark matter, modified gravity,
or MOND).  Instead, the simple combination of dissipational collapse, together
with angular momentum conservation produces the RAR. This means that even
galaxies where SN fails to regulate their star formation (or even where SN are
omitted altogether) fall on the observed relation.  This was the first published
demonstration of this in simulation, using untuned simulations made prior to the
publication of \citet{McGaugh2016}.

@@

\section{The Impact and Context of these Results}
Developing a versatile, accurate, resolution insensitve model for feedback has
been a challenge in galaxy simulations for decades \citep{Katz1992}.  While a
number of recent models have been developed that are able to produce galaxies
which match some observables, all of these models have relied on purely
numerical features to enhance the effectiveness of feedback and counter the
lossues due to limited resolution.  The \citet{Keller2014} model presented in Chapter 2 is
the first model of its kind that uses a first-principles approach to prevent
overcooling.  Beyond merely providing ``sufficient'' feedback, the superbubble model also
incorporates physics that previously have been omitted.  Thermal evaporation is
a key process for mixing cold ISM with hot feedback ejecta.  Prior to
\citet{Keller2014}, this process was completely ignored, and the local
mass-loading of feedback was set purely as a numerical parameter.
\citet{Rosdahl2016} illustrated this clearly, in a recent comparison project.
This paper implemented 5 popular feedback algorithms (simple thermal dumps; a
delayed cooling model similar to \citet{Agertz2013}; a kinetic model similar to
\citet{DallaVecchia2008}; a stochastic thermal model based on
\citet{DallaVecchia2012}; and a hybrid model from \citet{Kimm2015}) in the {\sc
RAMSES} code.  This allowed for a controlled test with isolated dwarf and Milky
Way analog galaxies. Each of these models, with ``fiducial'' parameter choices,
produced star formation rates that varied by nearly an order of magnitude in the
\citet{Kennicutt1998} star formation relation.  On top of that, the galaxies
showed marked morphological differences and average wind mass loadings that
varied by more than 4 orders of magnitude.  As we showed in \citet{Keller2015},
these winds are critical to the formation of galaxies like the Milky Way.  
In addition to the inter-model variation, \citet{Rosdahl2016} also found that the
numerical free parameters for each model had a vast impact on the resulting
galaxy's star formation rate, morphology, and outflow properties.  By building a
more conservative, physically motivated model where the local mass loading of
supernovae feedback is set by thermal evaporation, rather than numerically, we
can sidestep many of these issues.

@@

As we showed in \citet{Keller2015}, including thermal evaporation in simulations
of a Milky Way like galaxy will drastically change the effectiveness of
SN-driven galactic winds.  Removing gas from the galaxy is the only effective
mechanism for regulating star formation on cosmic timescales.  To prevent the
formation of bulges larger than the ones seen in the local universe, bulge
forming gas (low-angular momentum gas) must be removed from the ISM; because
SN-driven winds are most effective at high redshift, when this material is
mostly accreted, the outflows driven from the galaxy preferentially remove
bulge-forming gas.  A similar result was seen in simulations of dwarf galaxies
by \citet{Governato2010, Brook2011}, but \citet{Keller2015} is the first work to
show that bulgeless disc galaxies similar in mass to the Milky Way can be
produced through the same mechanism, and connect this with the regulation of
star formation.  An important conclusion of this study is that much of the past
work \citet{Stinson2013,Agertz2013,Hopkins2014} showing that SN feedback was
unable regulate star formation without the addition of ``early feedback'' from
radiation pressure, stellar winds, or photoionization was likely underestimating
the effectiveness of SN.  Since many of these studies used simpler, more
numerically-sensitive feedback models that also omitted thermal evaporation,
they were unable to effectively drive the correct amount of mass into hot, high
entropy gas that could leave the galaxy.  This study tells us that the
disc-dominant morphology and low stellar fraction in galaxies like our own all
arise from the same mechanism:  heavily mass loaded, high redshift winds.

@@

\section{Future Directions}
These results will be valuable for many new research projects.  The superbubble
model is a robust tool for simulating galaxies, and will become a key part of
future studies using the simulation codes {\sc Gasoline2} and {\sc ChaNGa}.  The
MUGS2 sample is a useful new set of simulations for answering questions
involving the evolution of Milky Way-like galaxies (as evidenced by our use of
it in Chapter 5).  These two resources will be valuable to both myself and other
researchers for years to come. The four publications presented here point
towards a number of questions I plan to answer during my postdoctoral research.

While observational evidence abounds for the existence of SMBHs
\citep{Kormendy2013}, and the impact of the AGNs they power
\citep{Veilleux2005}, there is still great uncertainty as to the details of how
they regulate their own growth, and the growth of the galaxies they live in.
\citet{Keller2016a} showed evidence that a transition occurs between galaxies
regulated by SN feedback to AGN feedback as they grow heavier than the Milky
Way.  How this handoff occurs remains widely unexplored.  Using my superbubble
feedback, along with new models for SMBH growth \citep{Hopkins2010} and
migration \citep{Tremmel2015}, we will for the first time be able to simulate
the growth of SMBHs in galaxies with first-principles, physically motivated
physics.  This will allow us to study the full gamut of galaxies that exist, and
study how the tight scaling relations between stellar bulges and SMBHs might
arise.

The CGM gas that surrounds galaxies is the interface between the star forming
disc and the galaxy's hot, gaseous halo (and the cosmic web beyond).  Any
material that accretes from the halo must first pass through the CGM, and any
material that leaves the ISM must do the same.  Despite the importance
of this component of the galaxy, observations of gas in the CGM are difficult.
This gas tends to be too cool \& diffuse to be a strong emitter of X-rays, and
absorption line studies require the lucky coincidence of a background quasar
\citep{Weiner2009}.  In addition to this, we know that the CGM contains complex,
multiphase structure, including cool neutral clouds \citep{Wakker1997},
molecular gas \citep{Stark1984}, and dust .  How this cold material can persist in a
CGM that is much hotter and that may be shearing past at supersonic velocities
is currently an open question.  Analytic calculations \& high resolution
simulations suggest that these clouds should be disrupted and mixed on
timescales far shorter than is required to ballistically launch them into the
CGM.  In light of this, why do we see these clouds?  They may be formed in-situ,
or may be launched by the fragmentation of superbubble shells, already
accelerated to high velocities during the momentum-conserving snowplow phase of
the bubble's growth.  High resolution simulations of superbubble breakout from
the ISM will be able to tell us if this is indeed the origin of these clouds.
Understanding the details of the multiphase CGM is key to
understanding how galaxies accrete and expel gas, as thermal instability in the
CGM (which depends heavily on its density, temperature, and metallicity) may be
the mechanism by which spiral galaxies today aquire the gas required to
form new stars \citep{Marasco2012}.  This work should allow us to understand the
origin of the relation between disc mass and outflow mass loadings seen in
\citet{Keller2016a}.

Large volume simulations like Illustris \citep{Vogelsberger2014b} and EAGLE
\citep{Schaye2015} can show how whole populations of galaxies evolved from the
earliest linear structures.  While these simulations contain models for star
formation, feedback from both stars and AGN, as well as radiative cooling, these
have all been fine-tuned to fit observed scaling relations.  This limits the
ability of these simulations to explain the origins of the observations they
have been tuned to fit.  My superbubble model contains no free/tuned parameters,
and accurately captures the evolution of feedback-heated gas as it evaporates
cool material that surrounds it.  It is the only feedback model currently in
existence that captures the important physical process of thermal conduction and
evaporation.  It will allow us to build a statistically significant sample of
physically realistic galaxies.  With first-principles, physically motivated
models for the unresolved physics in our simulations, we will be able to study
the actual physics involved in shaping both individual galaxies and the
populations that we observe. 
\bibliographystyle{mnras}
\bibliography{library}

>>>>

In this thesis we have explored the effects of SN feedback in the formation of 
galaxies like our own.  We introduced a novel model for SN feedback that
takes into account the important effects of previously ignored physics: the
evaporation of cold gas driven by thermal conduction.  This model allowed us to
see when SN can (and cannot!) regulate the flow of gas into and out of galaxies,
where it ultimately forms stars.  We have also shown that the current $\Lambda
CDM$ cosmological model is consistent with recent observations of galaxy
kinematics.

In Chapter 2, we presented a detailed description of the new superbubble model,
and implemented it in the SPH code {\sc Gasoline2}.  We rely on the strongly
self-limiting process of thermal evaporation \citep{Cowie1977}, where cold mass
is evaporated into a hot bubble at a rate strongly dependent on the temperature
of the hot bubble. This allows us to develop a new model for SN feedback, that gives
realistic estimates for cooling in unresolved hot bubbles, and accurately
calculates the mass loading of SN energy.  We demonstrated that this model is
insensitive to resolution, unresolved ISM structure, and uncertain (turbulent)
magnetic fields.  Finally, after investigating the behaviour of individual
bubbles, we showed that superbubble feedback was more effective at both
regulating star formation and at driving galactic winds.

Isolated disc simulations, like that shown in chapter 2, lack a full
cosmological history.  To really see how SN feedback can impact the overall
growth and history of a galaxy like the Milky Way, we needed to simulate the
galaxy from high redshift to the present, using a zoom-in technique like that
first introduced in \citet{Navarro1993}.  In chapter 3, we compared a Milky
Way-like galaxy, simulated four times with different feedback models (no
feedback, the older \citet{Stinson2006} blastwave model, and superbubble
feedback with $10^{51}\;\rm{erg}/SN$ and $2\times10^{51}\;\rm{erg}/SN$).  The
results of this comparison found that even though the galaxy massively
overproduced stars when simulated without feedback, or with blastwave feedback
(a result previously seen in \citealt{Stinson2010}) , the same SN energy, when
simulated using our new superbubble model, was able to produce a realistic
stellar mass fraction for the galaxy's entire history.  Not only did the galaxy
simulated with superbubble feedback have the correct stellar mass, we showed
that it also was effectively bulgeless, with a completely flat rotation curve.
These two results were ultimately caused by the same process.  At high redshift,
superbubble feedback efficiently drives highly mass loaded winds, expelling gas
from the ISM of the galaxy.  As the gas that forms a stellar bulge was primarily
accreted at high redshift, this meant that these winds preferentially removed
low angular momentum material, while preserving the gas with high angular
momentum.  Thus, superbubble feedback was able to naturally prevent both runaway
star formation and the formation of a bulge through these winds.

While a single galaxy can be a useful case study, multiple objects must be
studied in order to look at population-scale effects.  Chapter 4 extends the
results of chapter 3 by simulating an additional 17 objects, and uses these
simulations to examine if SN regulation can operate effectively in galaxies both
heavier and lighter than the Milky Way.  By creating a new sample of 18
simulated galaxies (the McMaster Unbiased Galaxy Simulations 2), we were able to
demonstrate a critical mass at which SN feedback breaks down as a regulator of
gas accretion and star formation.  Galaxies that exceed this mass, $(\sim
10^{12}\;\Msun)$, will produce more stars than real galaxies, and produce much
of these stars in a dense stellar bulge.  All of this arises due to a
fundamental relation between the mass loading of superbubble driven winds and
the mass of the galaxy (we found a relation between both disc and halo mass and
$\eta$).  When the escape velocity of the disc exceeds the sound speed of
superbubble-heated gas (which has a typical mass loading of $\eta=10$), only
outflows which have entrained less material are able to escape the galaxy,
leading to decreasing efficiency in ejecting material, and a shutdown of SN
regulation.  The fact that this shutdown occurs exactly where powerful AGN are
observed, and that it results in a vigorous transport of gas to the nucleus of
the galaxy make this result strong evidence that this shutdown acts as a 
``hand-off'' between SN and AGN feedback.

The MUGS2 simulations produced in chapter 4 contains a wealth of data
that is useful for future studies. Chapter 5 applied the MUGS2 sample of
galaxies we produced in \citet{Keller2016a} and used them to examine the radial
acceleration relation (RAR) that was derived by \citet{McGaugh2016} from
observations of the SPARC \citep{Lelli2016} catalog.  Contrary to the assertions
of some \citep{Milgrom2016}, the tight relation seen in the SPARC data does not
require new fundamental physics (such as self-interacting dark matter, modified
gravity, or MOND).  Instead, the simple combination of dissipational collapse,
together with angular momentum conservation produces the RAR. This means that
even galaxies where SN fails to regulate their star formation (or even where SN
are omitted altogether) fall on the observed relation.  This was the first
published demonstration of this in simulation, using untuned simulations made
prior to the publication of \citet{McGaugh2016}.

@@

\section{The Impact and Context of these Results}
Developing a versatile, accurate, resolution insensitve model for SN feedback has
been a challenge in galaxy simulations for decades \citep{Katz1992}.  While a
number of recent models have been developed that are able to produce galaxies
which match some observables, all of these models have relied on purely
numerical features to enhance the effectiveness of feedback and counter the
losses due to limited resolution.  The \citet{Keller2014} model presented in
Chapter 2 is the first model of its kind that uses a first-principles approach
to prevent overcooling.  Beyond merely providing ``sufficient'' feedback, the
superbubble model also incorporates physics that previously have been omitted.
Thermal evaporation is a key process for mixing cold ISM with hot feedback
ejecta.  Prior to \citet{Keller2014}, this process was completely ignored, and
the local mass-loading of feedback was set purely as a numerical parameter.
\citet{Rosdahl2016} illustrated this clearly, in a recent comparison project.
This paper implemented 5 popular feedback algorithms (simple thermal dumps; a
delayed cooling model similar to \citet{Agertz2013}; a kinetic model similar to
\citet{DallaVecchia2008}; a stochastic thermal model based on
\citet{DallaVecchia2012}; and a hybrid model from \citet{Kimm2015}) in the {\sc
RAMSES} code.  This allowed for a controlled test with isolated dwarf and Milky
Way analog galaxies. Each of these models, with ``fiducial'' parameter choices,
produced star formation rates that varied by nearly an order of magnitude in the
\citet{Kennicutt1998} star formation relation.  On top of that, the galaxies
showed marked morphological differences and average wind mass loadings that
varied by more than 4 orders of magnitude.  As we showed in \citet{Keller2015},
these winds are critical to the formation of galaxies like the Milky Way.  In
addition to the inter-model variation, \citet{Rosdahl2016} also found that the
numerical free parameters for each model had a vast impact on the resulting
galaxy's star formation rate, morphology, and outflow properties.  By building a
more conservative, physically motivated model where the local mass loading of
supernovae feedback is set by thermal evaporation, rather than numerically, we
can sidestep many of these issues.

Subgrid models are essential for including feedback from other mechanisms as
well.  Non-supernovae mechanisms for launching outflows and regulating star
formation are beginning to be studied with numerical simulations.  Radiation
pressure has been examined in a number of studies
\citep{Hopkins2014,Roskar2014,Agertz2015} using fairly simple treatments,
without full radiative transport.  These simulations have included various
models for feedback from SN and stellar winds, and have not produced consistent
conclusions as a result.  However, both \citet{Roskar2014} and
\citet{Agertz2015} found that the optical depths required for radiation pressure
to drive effective outflows produce unrealistic galaxy morphologies.  Cosmic
rays are beginning to be included in simulations with \citep{Girichidis2015} and
without \citep{Jubelgas2008,Booth2013} treatments for magnetohydrodynamics.
Most simulations have found that cosmic rays are unable to drive significant
outflows from Milky Way-like galaxies.  With a better constrained SN model,
these mechanisms can now be re-examined in the context of effective SN feedback.

With previous models for stellar feedback, both the qualitative behaviour as
well as the precise, quantitative effects have been strongly controlled by
poorly contrained numerical parameters.  This has made interpreting the results
of simulations difficult, as it is unclear what effects are a result of
the underlying physics and which are simply a result of the choice of parameters
used for the simulation.  Physics-driven, parameter-free models remove this
ambiguity, and allow us to produce results with greater confidence.

@@

As we showed in \citet{Keller2015}, including thermal evaporation in simulations
of a Milky Way-like galaxy will drastically change the effectiveness of
SN-driven galactic winds.  Removing gas from the galaxy is the only effective
mechanism for regulating star formation on cosmic timescales.  To prevent the
formation of bulges larger than the ones seen in the local universe, bulge
forming gas (low-angular momentum gas) must be removed from the ISM; because
SN-driven winds are most effective at high redshift, when this material is
mostly accreted, the outflows driven from the galaxy preferentially remove
bulge-forming gas.  A similar result was seen in simulations of dwarf galaxies
by \citet{Governato2010, Brook2011}, but \citet{Keller2015} is the first work to
show that bulgeless disc galaxies similar in mass to the Milky Way can be
produced through the same mechanism, and connect this with the regulation of
star formation.  An important conclusion of this study is that much of the past
work \citet{Stinson2013,Agertz2013,Hopkins2014} showing that SN feedback was
unable regulate star formation without the addition of ``early feedback'' from
radiation pressure, stellar winds, or photoionization was likely underestimating
the effectiveness of SN.  Since many of these studies used simpler, more
numerically-sensitive feedback models that also omitted thermal evaporation,
they were unable to effectively drive the correct amount of mass into hot, high
entropy gas that could leave the galaxy.  This study tells us that the
disc-dominant morphology and low stellar fraction in galaxies like our own all
arise from the same mechanism:  heavily mass loaded, high redshift winds.

@@

\section{Future Directions}
The results of this thesis have greatly clarified the effects of SN feedback,
but also raised some questions.  While we now know how SN regulate the
growth of stars in galaxies up to the mass of the Milky Way, details about the
transition to AGN regulation at high mass are still unclear.  The outflows that
are so key to shaping the galaxy, as we showed in chapter 3 and 4, are detailed,
mulitphase flows.  How exactly mass is entrained within these outflows and how
that material is recycled back into the disc will require further study as well.
Finally, the small sample of 18 galaxies we studied in chapter 4 and 5 are a
tiny fraction of the variety of galaxies seen in nature.  How does superbubble
feedback work to shape the scaling relations seen in galaxies both more and less
massive than the ones we have seen here?

While observational evidence abounds for the existence of SMBHs
\citep{Kormendy2013}, and the impact of the AGNs they power
\citep{Veilleux2005}, there is still great uncertainty as to the details of how
they regulate their own growth, and the growth of the galaxies they live in.
\citet{Keller2016a} showed evidence that a transition occurs between galaxies
regulated by SN feedback to AGN feedback as they grow heavier than the Milky
Way.  How this handoff occurs remains widely unexplored.  The results presented
here provide a robust baseline for the effects of SN feedback, which is
necessary to constrain before adding additional physics to the simulations.
Using my superbubble feedback, along with new models for SMBH growth
\citep{Hopkins2010} and migration \citep{Tremmel2015}, we will be able to
simulate the growth of SMBHs in galaxies with greater confidence, using
physically motivated feedback and accretion models.  This will allow us to study
the full gamut of galaxies that exist, and study how the tight scaling relations
between stellar bulges and SMBHs might arise.

One of the biggest questions raised in chapter 4 was the origin of the scaling
relation between outflow mass loadings and disc mass.  Observations of galactic
winds tell us that they are multiphase \citep{Stark1984,Wakker1997,Weiner2009},
containing ionized, neutral, and molecular gas.  This structure is unresolved
within our simulations, and may ultimately be important to the cooling rates and
recycling times for these outflows.  Detailed observations of outflowing
material in the CGM are difficult. This gas tends to be too cool \& diffuse to
be a strong emitter of X-rays, and absorption line studies require the lucky
coincidence of a background quasar \citep{Weiner2009}.  The presence of cold
clouds in particular is a significant problem for theories of galactic wind
launching.  Analytic calculations \& high resolution
simulations suggest that these clouds should be disrupted and mixed on
timescales far shorter than is required to ballistically launch them into the
CGM.  In light of this, why do we see these clouds?  They may be formed in-situ,
or may be launched by the fragmentation of superbubble shells, already
accelerated to high velocities during the momentum-conserving snowplow phase of
the bubble's growth.  These processes all take place on length scales far below
what is achievable in the cosmological simulations we have presented here.
High resolution simulations of superbubble breakout from
the ISM will be able to tell us if this is indeed the origin of these clouds.
Understanding the details of the multiphase CGM is key to
understanding how galaxies accrete and expel gas, as thermal instability in the
CGM (which depends heavily on its density, temperature, and metallicity) may be
the mechanism by which spiral galaxies today aquire the gas required to
form new stars \citep{Marasco2012}.

While the MUGS2 sample has been simulated with a robust, physically motivated
model for SN feedback, its sample size is small (only 18 galaxies), and covers a
limited range of halo masses ($\sim 4\times10^{11}-2\times10^{12}\;M_\odot$).
Modern large volume simulations like Illustris \citep{Vogelsberger2014b} and
EAGLE \citep{Schaye2015} contain $>10^6$ individual galaxies, spanning a range
of masses that include both galaxies lighter and more massive than those we have
studied here.  These larger sample sizes are essential to understanding how
whole populations of galaxies evolved from the earliest linear structures.
While these simulations contain models for star formation, feedback from both
stars and AGN, as well as radiative cooling, these have all been fine-tuned to
fit observed scaling relations.  This limits the ability of these simulations to
explain the origins of the observations they have been tuned to fit.  My
superbubble model contains no free/tuned parameters, and accurately captures the
evolution of feedback-heated gas as it evaporates cool material that surrounds
it.  It is the only feedback model currently in existence that captures the
important physical process of thermal conduction and evaporation.  It will allow
us to build a statistically significant sample of physically realistic galaxies.
With first-principles, physically motivated models for the unresolved physics in
our simulations, we will be able to study the actual physics involved in shaping
both individual galaxies and the populations that we observe. 
\bibliographystyle{mnras}
\bibliography{library}
